### 2012-12-08 inst/examples/may79-example.Rmd
example of resulting policy and simulation of GP vs true and "estimated" optimum.

```{r libraries}
require(nonparametric-bayes)
require(pdgControl)
require(ggplot2)
opts_knit$set(upload.fun = socialR::flickr.url)
```

@@

```{r}
x_grid = seq(0, 1.5 * K, length=101)
T <- 40
sigma_g <- 0.1
x <- numeric(T)
x[1] <- 1
```

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
gp <- gp_fit(obs, X, c(sigma_n=1, l=1))
```

@@

>>>>

```{r libraries}
require(pdgControl)
require(nonparametricbayes)
require(reshape2)
require(ggplot2)
require(data.table)
library(kernlab)
```

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA, tidy=FALSE)
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

@@

```{r}
x_grid = seq(0, 1.5 * K, length=101)
T <- 40
sigma_g <- 0.3
x <- numeric(T)
x[1] <- 1
```

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
gp <- gp_fit(obs, X, c(sigma_n=.9, tau = 1., l=.1), "kernlab")

```

@@

## Stochastic Dynamic programming solution based on the posterior Gaussian process:

```{r}
h_grid <- x_grid
```

GP Solution

```{r}
matrices_gp <- gp_transition_matrix(gp)
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```

Optimal solution

```{r}
matrices_true <- f_transition_matrix(f, p, x_grid, h_grid, sigma_g)
opt_true <- find_dp_optim(matrices_true, x_grid, h_grid, 20, 0, profit, delta=.01)
```

Optimal parametric solution in which a parameter is estimated with error

```{r}
matrices_estimated <- f_transition_matrix(f, p, x_grid, h_grid, sigma_g=0.01)
opt_estimated <- find_dp_optim(matrices_estimated, x_grid, h_grid, 20, 0, profit, delta=.01)
```

```{r policy_plot}
policies <- melt(data.frame(stock=x_grid, 
                            GP = x_grid[opt_gp$D[,1]], 
                            Exact = x_grid[opt_true$D[,1]],
                            Approx = x_grid[opt_estimated$D[,1]]),
                  id="stock")

policy_plot <- ggplot(policies, aes(stock, stock - value, color=variable)) +
  geom_point() + xlab("stock size") + ylab("escapement") 
policy_plot
```

We can see what happens when we attempt to manage a stock using this:

``` {r othernoise}
z_g <- function() rlnorm(1,0, sigma_g)
````

``` {r  simulate }
set.seed(1)
sim_gp <- ForwardSimulate(f, p, x_grid, h_grid, K, opt_gp$D, z_g, profit=profit)
set.seed(1)
sim_true <- ForwardSimulate(f, p, x_grid, h_grid, K, opt_true$D, z_g, profit=profit)
set.seed(1)
sim_est <- ForwardSimulate(f, p, x_grid, h_grid, K, opt_estimated$D, z_g, profit=profit)
````

```{r}
dat <- list(est = sim_est, gp = sim_gp, true = sim_true)
dat <- melt(dat, id=names(dat[[1]]))
dt <- data.table(dat)
setnames(dt, "L1", "method") 
```

``` {r  simplot}
ggplot(dt) + geom_line(aes(time,fishstock, color=method))
ggplot(dt) + geom_line(aes(time,harvest, color=method))
````

Total Profits

```{r}
c( gp = sum(sim_gp$profit), true = sum(sim_true$profit), est = sum(sim_est$profit))
```
